We need to purchase the following:
\begin{itemize}
\item \textbf{Memory (1000-1100 hkd)}

The details of memory can be found in Section~\ref{memoryOptions}. Most of the good brands cost similar at 1000 hkd for 16GB.

\item \textbf{Storage (1350 hkd)}

For storage, we need to purchase optical bay enclosure , superdrive enclosure and SSD. For details, refer to Section~\ref{opticalBayEnclosure} and Section~\ref{storageOptions}.The cost of optical bay enclosure with superdrive from a good brand must be around 350 hkd. The lower brands could cost 65 hkd. The cost of SSD varies more; we fix our expectation to 1000 hkd.

\item \textbf{Tools\footnotemark (120 hkd)}

The tools required for storage include all those that are required for memory. The details are mentioned in Section~\ref{storageOptions}. If a set is purchased from a good brand, the cost will be around 120 hkd.

\footnotetext{The price of tools is included in most packages that offer optical bay and superdrive enclosures. Our expected price for Storage is based on the price of some products, most of which include tools. The expected price of tools listed here is such when they are bought solely. One must be mindful of  \emph{double counting} here.}

\item \textbf{Keyboard, Mice and VGA adapter (700 hkd)}

The details about the peripherals are mentioned in Section~\ref{keyboardMiceVga}. The price of originals is 700 hkd. We fix our expectation to this price, but \emph{we will rigorously try to minimize the cost of peripherals of reasonable value when purchased from \market.}

\end{itemize}

After the purchasing ordeal is over, we need to install the products by following the information in the links discussed in Sections~\ref{memoryMethodology} and~\ref{storageMethodology}. We must also test the products to verify that they are functioning as they should according to the information in the links discussed in Section~\ref{postInstallVerification}.

We must also keep in mind the information discussed in Section~\ref{caretaking}. Heating of the logic board leading to fatal problems has happened before. We must never use our computer in a manner to aggravate the heating risks. There are some concerns that the battery may be fast depleted after installation of higher memory and SSD. We must keep the battery saving tips in mind. Further even after 16 GB RAM, memory can be exhausted by poor use of some applications. We must understand and follow the information on how to optimize memory use by applications.

We may also read and keep in mind other replacements of our \model, that may help in improving our experience. In future we may need to do them. Some of them are discussed in Section~\ref{futureConsideration}

