In this article we will explore various options to improve our computer --- \model.
We can sell our computer for about 4000 hkd at dcfever~\cite{dc} and buy a second hand for about 6-7000 hkd~\cite{dcmac,carousellmac}. However as there are risks involved, we prefer to just upgrade the system for about \upgradeprice hkd. When the system breaks, we can buy a cheap CPU temporarily and when time is right we will buy a new one. Care must be taken that the logic board doesn't overheat in future and the GPU problems that causes catastrophic trouble doesn't get repeated.

We consider upgrading memory, storage and other peripherals.
Memory up-gradation is straight forward where we will replace the two RAM in their slots. For storage, we will transfer the current Toshiba HDD to the optical bay and install a new SDD in the main bay.
We will consider the most valuable peripherals for up-gradation. 

The important aspects We will explore in this report are:
\begin{itemize}
\item \emph{Feasibility} of the new hardware. We will state the best---value models of hardware that are compatible with the motherboard so that it can be purchased for being mounted.

\item \emph{Heating} of the system after up-gradation. The GPU is vulnerable and has crashed leading to days of blackouts even in Hong Kong which has excellent Apple service. The replacement is not free now and the charge for new motherboard would be more than 4000 hkd. We will frame the cautions that must be taken so that the risk is ameliorated. 
\end{itemize}

