\subsection{Methodology for Memory}
\label{memoryMethodology}
We must refer to~\cite{ifixramreguide,owcramvid,youramvid} for installation. 

\subsection{Methodology for Storage}
\label{storageMethodology}
Some well known guides for setting up dual storage (main bay and optical bay) are~\cite{owcdualrep, youowcdualrep,ifixitdualrep}. There are also some guides for optical bay superdrive replacement with SDD~\cite{ifixitopsdrep,djttopsdrep}. Some guides for HDD/SDD replacement are~\cite{owchdsdrep,ifixithdsdrep}. 


\subsection{Post Installation verification}
\label{postInstallVerification}
According to ~\cite{macrumourramtest} memtest~\cite{memtest} should be done after installation. We plan to download the free version and run it. We also need to download mac os (.iso) to a pendrive and boot from it so full memory can be tested as advised~\cite{macrumourramtest}. We must also follow up with these sites~\cite{macworldramtest,turboframtest} to have a full test of RAM.

For SSD storage devices there is not much details about testing online. However there are some solutions for standard problems, which are rare. To test the actual speed an app can be downloaded from Mac App Store~\cite{itunesssdtest}. We may also follow some advice from this site~\cite{machowtotest}. \emph{In particular, we must check whether we need to enable TRIM depending on which device we have bought.}

\subsection{Care-taking in Future}
\label{caretaking}
 We have to take care of logic board burnout, its causes and precautions. Heating issue has to be dealt with rigorously. Some battery saving tips must also be read~\cite{owcsavebattery}. For RAM we must follow the instructions to reduce memory usage by applications like Chrome~\cite{zdnetchromeram}.

\subsection{Further Replacements for Consideration}
\label{futureConsideration}
\cite{ifixallguides} has a good list of feasible replacements for our MacBook Pro model. Some important ones are~\cite{ifixheatsinkguide, ifixlogicbdguide}. We have to take care of logic board burnout, its causes and precautions. Heating issue has to be dealt with rigorously. Some battery saving tips must also be read~\cite{owcsavebattery}.
